% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Shuangzhi Wu}

\basicInfo{
  \email{wushuangzhi2010@163.com} \textperiodcentered\ 
  \phone{(+86) 135-5288-1335} \textperiodcentered\ 
}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Harbin Institute of Technology (HIT)}, Harbin, China}{2015 -- Present}
\textit{Ph.D student} in Computer Science (CS)
\datedsubsection{\textbf{Harbin Institute of Technology (HIT)}, Harbin, China}{2013 -- 2015}
\textit{Master} in Computer Science (CS)
\datedsubsection{\textbf{Harbin Institute of Technology (HIT)}, Harbin, China}{2009 -- 2013}
\textit{B.S.} in Computer Science (CS)

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Microsoft Research Asia (MSRA)}}{May. 2014 - Present}
\role{Research Intern (Joint Ph.D. Program)}{Mentor: Dr. Dongdong Zhang}
Research intern in Nature Language Computing group. Conducting research on machine translation.

\datedsubsection{\textbf{Microsoft Research Asia (MSRA)}}{July. 2012 - June. 2013}
\role{Research Intern (Pre-Ph.D. Program)}{Mentor: Dr. Dongdong Zhang}
Research intern in Nature Language Computing group. Conducted research on spoken language processing.

\section{\faFilesO\ Project \& Publication}
\normalsize \textbf{Achieving Human Parity on Automatic Chinese to English News Translation} \\
\small \textbf{Shuangzhi Wu} as one of the major contributors\\
\small \textit{Project} https://arxiv.org/pdf/1803.05567.pdf

\normalsize \textbf{Dependency-to-Dependency Neural Machine Translation} \\
\small \textbf{Shuangzhi Wu}, Dongdong Zhang, Zhirui Zhang, Nan Yang, Mu Li, Ming Zhou\\
\small \textit{Journal paper of TASLP}

\normalsize \textbf{Improved Neural Machine Translation with Chinese Phonologic Features} \\
\small Jian Yang, \textbf{Shuangzhi Wu}, Dongdong Zhang, Ming Zhou, Zhongjun Li\\
\small \textit{Journal paper of NLPCC 2018}

\normalsize \textbf{Sequence-to-Dependency Neural Machine Translation} \\
\small \textbf{Shuangzhi Wu}, Dongdong Zhang, Nan Yang, Mu Li, Ming Zhou\\
\small \textit{Conference paper of ACL 2017 (long)}

\normalsize \textbf{Improved Neural Machine Translation with Source Syntax} \\
\small \textbf{Shuangzhi Wu}, Dongdong Zhang, Ming Zhou\\
\small \textit{Conference paper of IJCAI 2017}

\normalsize \textbf{Modeling Indicative Context for Statistic Machine Translation} \\
\small \textbf{Shuangzhi Wu}, Dongdong Zhang, Shujie Liu, Ming Zhou\\
\small \textit{under review as a conference paper of EMNLP 2017}

\normalsize \textbf{Efficient Disfluency Detection with Transition-based Parsing} \\
\small \textbf{Shuangzhi Wu}, Dongdong Zhang, Ming Zhou, Tiejun Zhao\\
\small \textit{Conference paper of ACL 2015 (long)}

\normalsize \textbf{Punctuation Prediction with Transition-based Parsing} \\
\small Dongdong Zhang, \textbf{Shuangzhi Wu}, Nan Yang, Mu Li\\
\small \textit{Conference paper of ACL 2013 (long)}

\normalsize \textbf{Regularizing Neural Machine Translation by Target-bidirectional Agreement} \\
\small Zhirui Zhang, \textbf{Shuangzhi Wu}, Shujie Liu, Mu Li, Ming Zhou, Enhong Chen\\
\small \textit{https://arxiv.org/pdf/1808.04064}

%\normalsize \textbf{Effective Soft-Adaptation for Neural Machine Translation} \\
%\small \textbf{Shuangzhi Wu}, Zhirui Zhang, Dongdong Zhang, Mu Li, Ming Zhou, Tiejun Zhao\\
%\small \textit{Under review} AAAI 2019 

%\normalsize \textbf{Source Dependency-Aware Transformer with Supervised Self-Attention} \\
%\small Chenyi Wang, \textbf{Shuangzhi Wu}, Shujie Liu, Dongdong Zhang, Ming Zhou\\
%\small \textit{Under review} AAAI 2019

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Professional Skills: Neural Machine Translation/Statistic Machine Translation/Spoken Language Processing/Dependency Parsing/Sequence-to-sequence modeling
  \item Programming Languages: C#/Python/C++/Java
  \item Platform: Linux/Windows
  \item Development: Cudnn/CUDA/Tensorflow
\end{itemize}

\section{\faHeartO\ Honors and Awards}
\datedline{The CCF Outstanding Undergraduate Award,OUA}{Dec. 2012}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
